---
title: "Assignment_2_Drew_Walker"
author: "Drew Walker"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks 

To provide insights to the public health official, you will perform the following tasks and/or 
answer the following questions:

1. Use the annotated data to design a supervised classification experiment. The experiment 
should involve training and evaluation. The standard supervised classification steps must be 
followed. (3 points) 

```{r, classification-model}

```


2. Use the same set of  tweets for comparing the classification performances of  at least 3 
classifiers. Which classifier is the best for classification? (3 points) 

```{r compare-classifiers}

```

3. Use the best-performing machine learning model to automatically classify all the unlabeled 
tweets. (2 points) 

```{r best-model}

```

4. Compare the distribution of  nonmedical use reporting tweets between the two locations (eg.., 
# of  reports, proportion of  tweets representing nonmedical use, population-adjusted report 
rate). (3 points) 
5. Compare the numbers of  nonmedical use representing tweets between opioids (eg., 
oxycodone), benzodiazepines (eg., alprazolam), and stimulants (eg., amphetamine mixed salts 
[aka. adderall]). (3 points) 
6. Compare the differences in nonmedical use among the different gender identities. 
7. Write a report (described below) for your experiments and results. (3 points) 
