---
title: "Assignment_1"
author: "Drew Walker"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(tidytext)
library(readxl)
library(readr)
library(tm)
library(lubridate)
library(here)
library(forcats)
library(dplyr)
library(ggplot2)
```

```{r read_data}
set1_raw <- read_excel("TADA_A1_set1.xlsx")
set1_raw <- set1_raw %>% 
  rename(date = date...2,
         text = date...4) %>% 
  mutate(real_id = row_number())
set2_raw <- read_csv("TADA_A1_set2.csv") %>% 
  rename(text = date_1) %>% 
  mutate(real_id = row_number())

set2_raw$date <- mdy(set2_raw$date)
```
# Tasks

To provide insights to the researcher, you will perform the following tasks and/or answer the
following questions:

1. What are the date ranges for the two sets? What information are provided in the CSV files?
a. Set 1 ranges from 2019-11-01 to 2020-01-30
b. Set 2 ranges from 2020-02-01 to 2020-04-29
```{r, date_ranges}

first(as.Date(set1_raw$date))
last(as.Date(set1_raw$date))

first(as.Date(set2_raw$date))
last(as.Date(set2_raw$date))

```

What are the languages in which tweets have been posted? (1 point)
```{r,detect_languages}
set1_langs <- set1_raw %>% 
  group_by(lang) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))
print(set1_langs)
set2_langs <- set2_raw %>% 
  group_by(lang) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))
print(set2_langs)
```

2. What is the total number of posts in set 1? What is the total in set 2? (1 point)
```{r, total_posts}
nrow(distinct(set1_raw,id))
nrow(distinct(set2_raw,id))
# Looks like the csv may have rounded a lot of the tweet ids in set2, rounding the number in excel. This could be an issue.

```
```{r, corpus}
set1_corpus <- VCorpus(VectorSource(set1_raw))
set2_corpus <- VCorpus(VectorSource(set2_raw))

full_text <- rbind(set1_raw,set2_raw)
```

3. How many tweets are there for methadone, Suboxone and fentanyl in total? Tip: sometimes
alternative expressions are used for substances (eg., fent for fentanyl). (2 points)
```{r,tweets_by_substance}
#Methadone

methadone_tweets <- full_text %>% 
  filter(lang== "en") %>% 
  filter(grepl('methadone|methdone|methad',text,ignore.case = TRUE)) %>% 
  filter(lang== "en") %>% 
  mutate(v= "methadone_tweets",
         analog = "NA")

#suboxone
suboxone_tweets <- full_text %>%
  filter(lang== "en") %>%
  filter(grepl('suboxone|subox|suboxne|suboxin|suboxen|saboxin|suboxine|suboxon|saboxone',text,ignore.case = TRUE)) %>% 
  mutate(v= "suboxone_tweets",
         analog = "NA")
#Fentanyl 
fentanyl_tweets <- full_text %>%
  filter(lang== "en") %>%
  filter(grepl('fentanyl|fent|fentanil|carfentanil|furanyl|acetyl|cyclopropyl',text,ignore.case = TRUE)) %>% 
  mutate(v= "fentanyl_tweets",
         analog = case_when(
           stringi::stri_detect_regex(text, "[Cc]arfentanil") ~ "carfentanil",
           stringi::stri_detect_regex(text, "[Ff]uranyl") ~ "furanyl",
           stringi::stri_detect_regex(text, "[Aa]cetyl") ~ "acetyl",
      stringi::stri_detect_regex(text, "[Cv]yclopropyl") ~ "cyclopropyl",
      TRUE ~ "NA"))
```

4. Are there fentanyl analogs that are also being discussed (eg., carfentanil)? (1 point)
```{r fentanyl_analogs}
analog_fentanyl_tweets <- fentanyl_tweets %>% 
  filter(grepl('carfentanil|furanyl|acetyl|cyclopropyl',text,ignore.case = TRUE)) %>% 
  group_by(analog) %>% 
  summarize(count=n())

analog_fentanyl_tweets %>%
  mutate(name = fct_reorder(analog, count)) %>%
  ggplot( aes(x=fct_reorder(analog,count), y=count)) +
    geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
    coord_flip() +
    xlab("") +
    theme_bw()
```
 getA
5. What are some of the topics that are most closely associated with each of the three
substances? Top 5-10 topics (if relevant) is acceptable. (2 points)

I had some issues with getAssoc, so I decided to do a tdm comparison of the different substance corpa. 
```{r, substance_topics}

full_annotated <- rbind(methadone_tweets,suboxone_tweets,fentanyl_tweets)

full_words <- full_annotated %>% 
  unnest_tokens(word, text) %>% 
  count(v,word,sort=TRUE) %>% 
  bind_tf_idf(word,v,n) %>% 
  arrange(desc(tf_idf))


full_words %>%
  group_by(v) %>%
  slice_max(tf_idf, n = 10) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(word, tf_idf), fill = v)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~v, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL)

```

6. Among the three substances and the tweets containing them, which two sets of tweets are
more similar than the other? There are several ways you can approach this problem. For
example, you could take a sample of tweets mentioning each of these substances and
represent each set as a single document. Or you may compare tweets from one set one-by-one
with a sample of the tweets from another set. Any reasonable approach for this task is
acceptable. Explain your method in the report (4 points).
```{r, substance_similarities}
fentanyl_text <- fentanyl_tweets$text
myStopWords <- stopwords()
fentanyl <- VCorpus(VectorSource(fentanyl_text)) %>% 
  tm_map(content_transformer(tolower)) %>% 
  tm_map(removeWords,myStopWords) %>% 
  tm_map(stemDocument)
fentanyl.dtm <- DocumentTermMatrix(fentanyl, control = list(weighting = weightTfIdf, stopwords = TRUE))

suboxone_text <- suboxone_tweets$text
suboxone <-  VCorpus(VectorSource(suboxone_text)) %>% 
  tm_map(content_transformer(tolower)) %>% 
  tm_map(removeWords,myStopWords) %>% 
  tm_map(stemDocument)
suboxone.dtm <- DocumentTermMatrix(suboxone, control = list(weighting = weightTfIdf, stopwords = TRUE))
methadone_text <- methadone_tweets$text

methadone <- VCorpus(VectorSource(methadone_text))%>% 
  tm_map(content_transformer(tolower)) %>% 
  tm_map(removeWords,myStopWords) %>% 
  tm_map(stemDocument)
methadone.dtm <- DocumentTermMatrix(methadone, control = list(weighting = weightTfIdf, stopwords = TRUE))

#Find assocs likely not able to grab assocs because of stemming? 
#tm::findAssocs(fentanyl,"fentanyl",.8)
#tm::findAssocs(fentanyl.dtm,"fentanyl",corlimit = .8)
#tm::findAssocs(methadone.dtm,"methadon",corlimit = .5)
#findAssocs(doc_term_matrix,"fentanyl",corlimit = .1)

all_texts <- c(methadone_tweets,suboxone_tweets,fentanyl_tweets)

all_texts_corpus <- Corpus(VectorSource(all_texts))%>% 
  tm_map(content_transformer(tolower)) %>% 
  tm_map(removeWords,myStopWords) %>% 
  tm_map(stemDocument)
doc_term_freq <- DocumentTermMatrix(all_texts_corpus)
#methadone vs suboxone
cosine(doc_term_freq[[1]],doc_term_freq[[2]])
#methadone vs fentanyl
cosine(doc_term_freq[[1]],doc_term_freq[[3]])
#suboxone vs fentanyl 
cosine(doc_term_freq[[2]],doc_term_freq[[3]])
```

Methadone and Suboxone Cosine similarity = 0.9275224
Methadone and Fentanyl Cosine Similarity = 0.02179706
Suboxone and Fentanyl Cosine Similarity = 0.009724012


7. Generate word clouds for each set, so that they can be shown to the researcher. (2 points)
# Fentanyl Corpus word cloud
```{r, fent-wordclouds}
library(wordcloud)
wordcloud(fentanyl, min.freq=10,max.words=200,scale=c(3,.1),random.order=FALSE,colors=brewer.pal(12,"Set3"))
```

# Methadone Corpus word cloud
```{r, methadone-wordclouds}
wordcloud(methadone, min.freq=10,max.words=200,scale=c(3,.1),random.order=FALSE,colors=brewer.pal(12,"Set3"))
```

```{r, suboxone-wordclouds}
wordcloud(suboxone, min.freq=10,max.words=200,scale=c(3,.1),random.order=FALSE,colors=brewer.pal(12,"Set3"))
```
8. Generate appropriate time-series figures to compare how the frequencies of mentions of
these substances differ. (2 points)
```{r, time_series}
ts_full_annotated <- full_annotated %>% 
  mutate(day = as.Date(date),
         month = month(day),
         year = year(day)) %>% 
  group_by(day,v) %>% 
  summarize(count = n())
  
library(viridis)
tweets_per_day <- ggplot(ts_full_annotated, aes(day, count,group=v, color=v)) +
  geom_line()+
  scale_color_viridis(discrete = TRUE) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(y = "Tweets per Day", title = "Types of Substance Mentioned in Tweets")
tweets_per_day
```

9. Find the top 10 most frequent bigrams in each of the three sets. Plot a bar chart for these. (2
points)’
```{r, most_frequent_bigrams}

```

10. Write a report (described below) for your experiments and results. (3 points)
